### 2020-07-19 article.tex
Change one keyword, change Fig 6 to Table 1, and modify one sentence in the conclusions

% REQUIRED
\begin{keywords}
  Krylov methods, domain decomposition preconditioners, distributed computing
\end{keywords}

@@

This continuous equation is discretized with third-order Lagrange finite elements using FreeFEM. The script is available at \url{https://github.com/prj-/jolivet2020petsc}. The following timings and convergence histories have been obtained on $2{,}304$ processes of Ir\`ene, for solving a problem of dimension \pgfmathprintnumber{74618461}. By default, SLEPc applies at most 5 iterations of GMRES on each column of a so-called set of active columns. Since the option \pk{-eps\_lobpcg\_blocksize 40} is used for computing 20 eigenpairs, the size of the set varies between 40 to 1. This size corresponds to the number of right-hand sides in systems that will be solved throughout LOBPCG iterations. Instead of using \pk{KSPGMRES}, which does not handle blocking, \pk{KSPHPDDM} is used, with the pseudo-block GMRES. That means that, assuming the size of the set of active columns is 40, one LOBPCG iterations implies doing at most 5 GMRES iterations with 40 vectors simultaneously, using \pk{MatProductNumeric} and \pk{PCMatApply}, instead of doing at most $40\times 5$ successive GMRES iterations, using \pk{MatMult} and \pk{PCApply}. Results are gathered in~\cref{fig:lobpcg}. In the first line, the numbers of outer LOBPCG iterations are reported with the three different inner preconditioners mentioned above. \pk{PCASM} is known to yield a preconditioned operator whose condition number grows as the number of subdomains, here processes, increases. Thus, the number of outer iterations is higher than with \pk{PCHPDDM} or \pk{PCGAMG} since the inner solves are not converging to meaningful solutions in just 5 iterations. The multilevel preconditioners perform similarly, since the difference in the number of outer iterations is minimal (1). The second and third lines represent the number of times \pk{PCApply} and \pk{PCMatApply} are called. Since \pk{PCGAMG} does not handle blocking, at each pseudo-block GMRES iteration, \pk{PCApply} is called on each single active column. \pk{PCASM} and \pk{PCHPDDM} handle blocking, so only rely on \pk{PCMatApply}. In the fourth line, the time spent setting up the preconditioners is given. \pk{PCASM} is extremely cheap but not very robust numerically, while both multilevel preconditioners have a similar setup time. Eventually, in the last line, the time spent in the full eigensolve is given. Clearly, having both a \pk{KSP} and a \pk{PC} which can deal with multiple vectors efficiently is mandatory to achieve reasonable performance with such an outer solver that heavily relies on blocking.

@@

\begin{figure}[h!]

@@

\caption{Performance of \pk{EPSLOBPCG} with three different inner preconditioners: \pk{PCASM} and \pk{PCHPDDM}, which utilize \pk{PCMatApply}, and \pk{PCGAMG}, which utilizes \pk{PCApply}.\label{fig:lobpcg}}

@@

Concerning SLEPc, we plan to implement new solvers or extend existing ones to
further exploit block solve primitives, for instance, block
Krylov--Schur~\cite{zhou2008block}. The current code for Arnoldi iterations
would then handle block Arnoldi iterations.

>>>>

% REQUIRED
\begin{keywords}
  Krylov methods, domain decomposition preconditioners, distributed-memory parallel computing
\end{keywords}

@@

This continuous equation is discretized with third-order Lagrange finite elements using FreeFEM. The script is available at \url{https://github.com/prj-/jolivet2020petsc}. The following timings and convergence histories have been obtained on $2{,}304$ processes of Ir\`ene, for solving a problem of dimension \pgfmathprintnumber{74618461}. By default, SLEPc applies at most 5 iterations of GMRES on each column of a so-called set of active columns. Since the option \pk{-eps\_lobpcg\_blocksize 40} is used for computing 20 eigenpairs, the size of the set varies between 40 to 1. This size corresponds to the number of right-hand sides in systems that will be solved throughout LOBPCG iterations. Instead of using \pk{KSPGMRES}, which does not handle blocking, \pk{KSPHPDDM} is used, with the pseudo-block GMRES. That means that, assuming the size of the set of active columns is 40, one LOBPCG iterations implies doing at most 5 GMRES iterations with 40 vectors simultaneously, using \pk{MatProductNumeric} and \pk{PCMatApply}, instead of doing at most $40\times 5$ successive GMRES iterations, using \pk{MatMult} and \pk{PCApply}. Results are gathered in~\cref{tab:lobpcg}. In the first line, the numbers of outer LOBPCG iterations are reported with the three different inner preconditioners mentioned above. \pk{PCASM} is known to yield a preconditioned operator whose condition number grows as the number of subdomains, here processes, increases. Thus, the number of outer iterations is higher than with \pk{PCHPDDM} or \pk{PCGAMG} since the inner solves are not converging to meaningful solutions in just 5 iterations. The multilevel preconditioners perform similarly, since the difference in the number of outer iterations is minimal (1). The second and third lines represent the number of times \pk{PCApply} and \pk{PCMatApply} are called. Since \pk{PCGAMG} does not handle blocking, at each pseudo-block GMRES iteration, \pk{PCApply} is called on each single active column. \pk{PCASM} and \pk{PCHPDDM} handle blocking, so only rely on \pk{PCMatApply}. In the fourth line, the time spent setting up the preconditioners is given. \pk{PCASM} is extremely cheap but not very robust numerically, while both multilevel preconditioners have a similar setup time. Eventually, in the last line, the time spent in the full eigensolve is given. Clearly, having both a \pk{KSP} and a \pk{PC} which can deal with multiple vectors efficiently is mandatory to achieve reasonable performance with such an outer solver that heavily relies on blocking.

@@

\begin{table}[h!]
\caption{Performance of \pk{EPSLOBPCG} with three different inner preconditioners: \pk{PCASM} and \pk{PCHPDDM}, which utilize \pk{PCMatApply}, and \pk{PCGAMG}, which utilizes \pk{PCApply}.\label{tab:lobpcg}}

@@

\end{table}

@@

Concerning SLEPc, we plan to implement new solvers or extend existing ones to
further exploit block solve primitives, for instance, block
Krylov--Schur~\cite{zhou2008block}. The current code for Arnoldi iterations
would then handle block Arnoldi iterations, and shift-and-invert solves would
operate on the whole block instead of column by column.
